### 2021-03-18 paper.Rmd
Updated interpolation part based on notes from Sherry

For any method we need to ensure that each projection along the interpolated path is still orthonormal. In the case of one-dimensional projections, the set of bases traces a path along the surface of a hypersphere of radius one, as illustrated in Figure (XXX adding an illustration using ferrn). For higher-dimensional projections this is generalized and we find the path along the surface of a torus instead (need to check about this with Sherry).

> figure 5 diagram illustrating geodesic interpolation

>>>>

For any method we need to ensure that each projection along the interpolated path is still orthonormal. As explained above this means a tour path is a trace along a Stiefel manifold. In the case of one-dimensional projections, the set of bases traces a path along the surface of a hypersphere of radius one, as illustrated in Figure \ref{fig:notation-target-gen}, and for two-dimensional projections projections fall onto a torus shape. We can use a tour to visualize such a path, as shown in Figure \ref{fig:interpolation-2d}.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/notation-2d-space.pdf}
\caption{Still views of a tour showing the space of possible two-dimensional projections as a torus shape in grey, and the trace of two short paths obtained via geodesic interpolation traced in color.}
\label{fig:interpolation-2d}
\end{figure}
